Considering scale in multilayer animal social networks

### 2020-06-17 paper/manuscript.Rmd
Disc p 1 and 2

Our results highlight the influence of social, spatial and temporal scale on
multilayer networks. For social scale, we found individuals became more
connected with increasing spatial distance threshold. Increasing land cover
resolution lead to a decrease in availability of patchy and rare habitats and, 
<!--QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
Could you just say 'less common' or even just 'patchy'?-->
correspondingly, lower connectivity of individuals in these habitats. Temporal
windows highlighted clear periods of increased sociality among individuals.
Finally, increasing number of observations lead to a general stabilizing in network
metrics. As such, scale is inherently tied to the generation  of multilayer
networks and metrics evaluating them, as well as the individual layers that make
them up.
<!--QW: I will pre-empt Eric and say I think this paragraph could maybe not mention the results at all. 
You could focus on just talking about the importance of scale for behavioural and spatial ecology.
Why is it important and what are the more broadly applicable ideas that lead us to this paper? 
Maybe keep this little summary paragraph for now - I think likely we could integrate what I describe 
above with what you already have-->

Monolayer network approaches have been increasingly used to link social network
position with individual fitness, including in primates [@Brent_2017;
@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
for understanding fitness consequences in the context of social network
positions <!-- TODO JWT check --> [@Almeling_2016; @Berger_2015; @Brent_2017;
@Holekamp_2011]. Defining the social scale to generate networks is an
essential consideration for social network analysis <!-- with direct impacts on
outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
social networks generated using GPS location data require using a social scale,
specifically a spatial distance threshold, to define social associations. We
found increasing individual graph strength across three habitat types with
increasing spatial distance threshold (Figure \@ref(fig:socres)). In addition,
habitat layers differed in their response to spatial distance threshold, with
open and forage with a larger increase in graph strength and greater variation
across individuals. These results emphasize that multilayer network metrics are
directly influenced by social scale, in this case the spatial distance
threshold.

>>>>

Our results highlight the influence of social, spatial and temporal scale on
multilayer networks. For social scale, we found individuals became more
connected with increasing spatial distance threshold. Increasing land cover
resolution lead to a decrease in availability of patchy and rare habitats and, 
<!--QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
Could you just say 'less common' or even just 'patchy'?-->
correspondingly, lower connectivity of individuals in these habitats. Temporal
windows highlighted clear periods of increased sociality among individuals.
Finally, increasing number of observations led to a general stabilization in network
metrics. As such, scale is inherently tied to the generation  of multilayer
networks and metrics evaluating them, as well as the individual layers that make
them up.
<!--QW: I will pre-empt Eric and say I think this paragraph could maybe not mention the results at all. 
You could focus on just talking about the importance of scale for behavioural and spatial ecology.
Why is it important and what are the more broadly applicable ideas that lead us to this paper? 
Maybe keep this little summary paragraph for now - I think likely we could integrate what I describe 
above with what you already have-->

Monolayer network approaches have been increasingly used to link social network
position with individual fitness, including in primates [@Brent_2017;
@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
for understanding fitness consequences in the context of social network
positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
@Holekamp_2011]. Defining the social scale to generate networks is an
essential consideration for social network analysis <!-- with direct impacts on
outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
social networks generated using GPS location data require using a social scale,
specifically a spatial distance threshold, to define social associations. We
found increasing individual graph strength across three habitat types with
increasing spatial distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
habitat layers differed in their response to spatial distance threshold, with
open and forage with a larger increase in graph strength and greater variation
across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
directly influenced by social scale, in this case the spatial distance
threshold.
